A systematic search for transiting planets using \KT

### 2015-02-07 ms.tex

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission (Cite-Ricker 14).
\tess will feature pointing precision of $\sim 3$ arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

@@

In \KT, we will not be able to rely on any of these techniques to
characterize systems \textit{en masse}.
There are typically only a handful of transits, meaning differences
between ``odd'' and ``even'' transits must be large to create
a significant difference.
Searching for ellipsoidal varaitions is hindered by the short time
baseline and the increased photometric uncertainty in \KT\ data.
Searching for centroid variations is also more difficult in \KT:
to measure a centroid offset, one must know where the centroid is
supposed to be.
Predicting a centroid position is trivial with \kepler\ data due to the
remarkably stable pointing of the instrument.
With \KT\ this is only possible if one understands the pointing of the
spacecraft at a specific time.
In theory, this is possible: the spacecraft is a rigid body, and by measuring
the mean motion of stars across the detector over time, the
Euler angles can be inferred at all times.
However, properly measuring positions of stars is a difficult problem:
the centroid depends sensitively on the (unknown) flat field, which must
be simultaneously inferred.
Therefore, false positives caused by background eclipsing binaries which could
be identified as such by \kepler\ data alone will be much more difficult to
distinguish in \KT\ data, making high-contrast adaptive optics images of
planet candidates an essential follow-up tool.

@@

>>>>

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission (Cite-Ricker 14).
\tess\ will feature pointing precision of \sim 3 arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

@@

In \KT, we will not be able to rely on any of these techniques to
characterize systems \textit{en masse}.
There are typically only a handful of transits, meaning differences
between ``odd'' and ``even'' transits must be large to create
a significant difference.
Searching for ellipsoidal varaitions is hindered by the short time
baseline and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently
than in the original \kepler\ mission.
In that data, centroid positions are measured for the data during and out of
transit by coadding all the relevant frames in each quarter.
Such a technique is feasible due to the remarkably stable pointing of the
instrument.
Searching for centroid variations with this method is more difficult in \KT:
to measure a centroid offset, one must know where the centroid is
supposed to be.
With \KT\ this is only possible if one understands the pointing of the
spacecraft at a specific time.
In theory, this is possible: the spacecraft is a rigid body, and by measuring
the mean motion of stars across the detector over time, the
Euler angles can be inferred at all times.
However, properly measuring positions of stars is a difficult problem:
the centroid depends sensitively on the (unknown) flat field, which must
be simultaneously inferred.

While the traditional method to measure centroids is significantly more
challenging with \KT\ data, we have developed an alternative method
to identify centroid offsets during transits in our data.
In our data analysis, we model the systematics in the light curve
caused by spacecraft motion, constrained by the ensemble of all stars in
the field of view.
The same can be done with the positions of each star, instead of the flux,
as a function of time.
In this case, for each candidate, we model the time series of centroid
positions in each dimension as a linear combination of our PCA basis vectors
plus a shift of unknown amplitude during transit events.
Such a technique enables us to measure the centroid shift during transit and
quantify an uncertainty of the size of this shift.

%Therefore, false positives caused by background eclipsing binaries which could
%be identified as such by \kepler\ data alone will be much more difficult to
%distinguish in \KT\ data, making high-contrast adaptive optics images of
%planet candidates an essential follow-up tool.

@@

{\it Facilities:} \facility{Kepler}
